### 2020-12-07 supp.tex
fix supp

@@

The intrinsic generation-interval distribution $\gdist(\tau)$ provides a link between $r$ and \Ro via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{equation}
\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) \gdist(\tau) \dtau\,.
\end{equation}
In this section, we prove that the initial forward serial-interval distribution $f_0(\tau)$ also estimates the same \Ro from $r$, except that integral extends to $\tau=-\infty$ rather than beginning at $\tau=0$, because serial intervals can be negative:
\begin{equation}
\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \dtau\,.
\label{eq:ptarget}
\end{equation}
Here, the initial forward serial-interval distribution $f_{0}(\tau)$ is defined as:
\begin{equation}
f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\,,
\label{eq:fdist}
\end{equation}
where $h$ is the joint probability distribution describing the
intrinsic generation-interval distribution $g$ and the intrinsic
incubation period distribution $\idist$ (see \eref{marginal} in the
main text), and the normalization constant $\phi$ is determined by the
requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.

>>>>

\renewcommand{\theequation}{S.\arabic{equation}}

@@

The intrinsic generation-interval distribution $\gdist(\tau)$ provides a link between $r$ and \Ro via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{equation}
\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) \gdist(\tau) \dtau\,.
\end{equation}
In this section, we prove that the initial forward serial-interval distribution $f_0(\tau)$ also estimates the same \Ro from $r$, except that integral extends to $\tau=-\infty$ rather than beginning at $\tau=0$, because serial intervals can be negative:
\begin{equation}
\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \dtau\,.
\label{eq:ptarget}
\end{equation}
Here, the initial forward serial-interval distribution $f_{0}(\tau)$ is defined as:
\begin{equation}
f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\,,
\label{eq:fdist}
\end{equation}
where $h$ is the joint probability distribution describing the
intrinsic generation-interval distribution $g$ and the intrinsic
incubation period distribution $\idist$ (see Eq.~(15) in the
main text), and the normalization constant $\phi$ is determined by the
requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
